---
output: rmarkdown::github_document
---

`keybase` : Tools to Work with the 'Keybase' 'API'

'Keybase' (<https://keybase.io>) is a directory of people and public keys and provides methods for obtaining public keys, validating users and exchanging files and/or messages in a secure fashion. Tools are provided to search for and retrieve information about 'Keybase' users, retrieve and import user public keys and list and/or download files.

There's also a thin but useful R wrapper around many of they `keybase` command-line utility functions.
    
The following functions are implemented:

- `kb_discover`:	Check Keybase membership and retrieve basic user info
- `kb_file_exists`:	See if a file exists
- `kb_get_public_keys`:	Retrive the public key(s) for a given user
- `kb_list_files`:	List directory path contents in a Keybase user's public folder
- `kb_lookup`:	Retrieve info on Keybase user(s)
- `kb_raw_url`:	Turn a user + path into a Keybase "raw" URL
- `kb_read_file`:	Read a resource (file) from a Keybase public folder
- `kb_cmd`:	Execute a keybase command-line command
- `kb_encrypt_file`:	Encrypt a file
- `kb_decrypt_file`:	Decrypt a file
- `kb_encrypt_msg`:	Encrypt a message
- `kb_decrypt_msg`:	Decrypt a message
- `kb_followers`:	Get keybase followers
- `kb_following`:	Get who you're following on keybase
- `kb_ping`:	Test connectivity to the keybase server

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/keybase")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

### Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(keybase)
library(tidyverse)

# current verison
packageVersion("keybase")

kb_ping()

kb_discover(twitter=c("hrbrmstr", "_inundata", "briandconnelly"), github="bearloga")

kb_discover(twitter=c("sckottie", "_inundata", "briandconnelly"), kb_usernames_only=TRUE)

kb_lookup("karthik")

kb_list_files("marcopolo")

kb_list_files("marcopolo", pattern="\\.txt")
```

### Safe(r) data sharing

```{r}
kb_list_files("hrbrmstr", "data")

kb_file_exists("hrbrmstr", "index.md")

kb_file_exists("https://hrbrmstr.keybase.pub/data/Rlogo.pngd")

kb_raw_url("hrbrmstr", "data/Rlogo.png")

kb_file_exists("hrbrmstr", "data/Rlogo.png")

kb_file_exists(kb_raw_url("hrbrmstr", "data/Rlogo.png"))

kb_read_file("hrbrmstr", "data/mtcars.csv")

kb_read_file("hrbrmstr", "data/mtcars.json")

# need (for now) to use the "raw" URL for things `rio::import()` can't natively read

kb_list_files("hrbrmstr", "data", pattern = ".*.png") %>% 
  select(raw_url)

magick::image_read("https://hrbrmstr.keybase.pub/data/Rlogo.png")
```

### Test Results

```{r message=FALSE, warning=FALSE, error=FALSE}
library(keybase)
library(testthat)

date()

test_dir("tests/")
```

