---
output: rmarkdown::github_document
---

`keybase` : Tools to Work with the 'Keybase' 'API'

'Keybase' (<https://keybase.io>) is a directory of people and public keys and provides methods for obtaining public keys, validating users and exchanging files and/or messages in a secure fashion. Tools are provided to search for and retrieve information about 'Keybase' users, retrieve and import user public keys and list and/or download files.
    
The following functions are implemented:

- `kb_discover`:	Check Keybase membership and retrieve basic user info
- `kb_get_public_keys`:	Retrive the public key(s) for a given user
- `kb_list_files`:	List files/directories in a user's public folder
- `kb_lookup`:	Retrieve info on Keybase user(s)

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/keybase")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

### Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(keybase)

# current verison
packageVersion("keybase")

kb_discover(twitter=c("hrbrmstr", "_inundata", "briandconnelly"), github="bearloga")

kb_discover(twitter=c("sckottie", "_inundata", "briandconnelly"), kb_usernames_only=TRUE)

kb_lookup("karthik")

kb_list_files("marcopolo")

kb_list_files("marcopolo", pattern="\\.txt")
```

### Test Results

```{r message=FALSE, warning=FALSE, error=FALSE}
library(keybase)
library(testthat)

date()

test_dir("tests/")
```

